Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-02-21 paper/ms.tex
some words about transit example [ci skip]

>>>>

In this example, we inject the signal of a simulated exoplanet transit into a
real \kepler\ light curve and then demonstrate that we can recover the true
physical parameters of the exoplanet while modeling the stellar variability
using \celerite.
This example is different from all the previous examples because in this case,
we are uninterested in the inferred parameters of the covariance model.
Instead, we're interested in inferring constraints on the parameters of the
mean model.
In \eq{gp-likelihood} these parameters are called $\bvec{\theta}$ and in this
example, the mean function $\mu_\bvec{\theta}(t)$ is a limb-darkened transit
light curve \dfmtodo{CITE MA} parameterized by a period $P$, a transit
duration $T$, a phase or epoch $t_0$, an impact parameter $b$, the radius
of the planet in units of the stellar radius $R_P/R_\star$, and several
parameters describing the limb-darkening profile of the star \dfmtodo{CITE}.
